%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% Important notes:
% This template needs to be compiled with XeLaTeX and the bibliography, if used,
% needs to be compiled with biber rather than bibtex.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[a4paper]{friggeri-cv} % Add 'print' as an option into the square bracket to remove colors from this template for printing
\usepackage{pifont}
\usepackage{marvosym}
\usepackage{wasysym}
\begin{document}

\header{Simon }{Hollingshead}{Site Reliability Engineer at Google $\cdotp$ BA (Hons., Cantab.)}

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------
\begin{aside} % In the aside, each new line forces a line break
\section{contact}
\href{mailto:jobs@simonhollingshead.com}{\footnotesize{jobs@simonhollingshead.com}}
\href{https://linkedin.com/in/shollingshead}{\footnotesize{linkedin.com/in/shollingshead}}
+44 7580 619 346
~
{\textbf{Initially contact me by:}}
Email, InMail \ding{51}
Phone \ding{55}
~
{\textbf{Latest CV always at:}}
\href{https://simonhollingshead.com/cv/}{\footnotesize{simonhollingshead.com/cv/}}
~
\section{skills}
C++
Communication
Cybersecurity
Incident Response
Monitoring Design
System Design
Troubleshooting
~
\section{interests}
CTF Competitions
Economics
Scavenger Hunts
Security Conferences
Space
Walking
\end{aside}

%----------------------------------------------------------------------------------------
%	BODY SECTIONS
%----------------------------------------------------------------------------------------

\section{experience}

\begin{entrylist}
\entry
{{\footnotesize Since Sep `17}}
{Site Reliability Engineer at Google}
{London, UK}
{\emph{Production Security Labs SRE (Since May 2022)} 

Developing and implementing designs for horizontal security improvements
to the entire Google production infrastructure.  Requires big-picture thinking and
consideration of how to execute such changes safely with the minimal possible
companywide cost to productivity.

~

\emph{Ads Quality Infrastructure SRE (Sep 2017 -- May 2022)}

Service owner for a large backend product in Google Ads.  Executed large
projects to increase developer velocity, improve turnup speed and
safety, and improve time to remediation during incidents through changes
to the monitoring.  Primary on-call during multiple major Ads outages, requiring troubleshooting
and incident response skills.

~

}
\entry
{{\footnotesize Sep `14 -- Aug `17}}
{Software Engineer at BAE Systems Applied Intelligence}
{Guildford, UK}
{\emph{Systems Engineering, Commercial Solutions Enterprise Managed Security}

\emph{(May 2015 -- Aug 2017)}

Built systems used by our Security Operations Centre.  Generally involved
either system administration tasks, building `glue' applications to plumb
together multiple commercially-available software products to meet our
needs, or writing our own services where no such tool existed (e.g.\ for
loading specialised datasets into ElasticSearch).

~

\emph{Rules and Analytics, Commercial Solutions Enterprise Managed Security}

\emph{(Sep 2014 -- May 2015)}

Wrote rules which identified anomalous activity from within terabytes of data
daily using Hadoop MapReduce and Apache Hive.  Learned how to consider
a customer's needs when producing analytics directly consumed by a remote
team (the Security Operations Centre) and how to collaborate to
provide richer information and reduce false positives.  Produced many
tools which just became a standard part of Operations' toolkit to monitor, rerun
or backfill data into the analytics system.
}
\end{entrylist}

\section{education}

\begin{entrylist}
%------------------------------------------------
\entry
{2011 -- 2014}
{BA Hons. {\normalfont in Computer Science (Class }2.i{\normalfont )}}
{University of Cambridge}
{
~

A full academic history is provided at \href{https://simonhollingshead.com/academic-records/}{https://simonhollingshead.com/cv/}.
}
\end{entrylist}

\section{other certifications}
\begin{entrylist}
\entry
{Oct 2016}
{Professional Scrum Developer I}
{from Scrum.org}
{}
\end{entrylist}
\end{document}

